### 2023-09-17 main.tex
Exchange Upadate

We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename its elements, each of them acting on the quantum space $V$, has follows
\begin{comment}
	\begin{equation}
		U_{0}(x)=\begin{pmatrix}
			D_{11}(x)&B_{2}(x)&\ldots&B_{N}(x)\\
			C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
			\vdots&\vdots&\ddots&\vdots\\
			C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
		\end{pmatrix}
	\end{equation}
\end{comment}
\begin{equation}
	U_{0}(x)=\begin{pmatrix}
		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
		\vdots&\vdots&\ddots&\vdots&\vdots\\
		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
	\end{pmatrix}
\end{equation}
The exchange relations for the elements of the above matrix can be found using \eqref{RURU} and they read:
\begin{itemize}
	\item for every $i\in\{1,\ldots,N-1\}$
	\begin{equation}\label{EX1}
		\begin{split}
			D_{N,N}(y)B_{i}(y)&=f(x,y)D_{N,N}(x)B_{i}(y)+f_{1}(x,y)B_{i}(x)D_{N,N}(y)\\&+f_{2}(x,y)\left(B_{i}(x)D_{i,i}(y)+\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)\right)
		\end{split}	
	\end{equation}
	\begin{equation}\label{EX2}
		\begin{split}
			D_{i,i}(x)B_{i}(x)&=h(x,y)B_{i}(y)D_{i,i}(x)+h_{1}(x,y)B_{i}(x)D_{i,i}(y)\\&+h_{2}(x,y)B_{1}(x)D_{N,N}(y)+h_{3}(x,y)B_{i}(y)D_{N,N}(x)\\&+\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)+h_{4}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(y)D_{k,i}(x)
		\end{split}
	\end{equation}
	\item  for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
	\begin{equation}\label{EX3}
		\begin{split}
			D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)-B_{i}(x)D_{i,i}(y)\right)
			\\&+
			\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{N,N}(y)-B_{i}(y)D_{N,N}(x)\right)
			\\&+
			h_{1}(x,y)\left(B_{j}(x)D_{j,i}(y)-B_{j}(y)D_{i,j}(x)\right)
			\\&+
			\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\,k\neq i,j}\left(B_{k}(y)D_{k,i}(x)-B_{k}(x)D_{k,i}(y)\right)
		\end{split}
	\end{equation}

\end{itemize}
where
\begin{align}
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\end{align}
\subsection{Charges}
The transfer matrix $T^{\Delta}(x)$ reads
\begin{equation}
	\begin{split}
		T^{\Delta}(x)=%tr_{0}&\left(\begin{pmatrix}
			%-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
		%	0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
		%	\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		%	0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
		%	0&0&0&\ldots&0&N+x
	%	\end{pmatrix}\right.
	%	\;\;\;\begin{pmatrix}
	%		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
	%		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
	%		\vdots&\vdots&\ddots&\vdots&\vdots\\
	%		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
	%		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
	%	\end{pmatrix}\right)\\
	%=&
	(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
	\end{split}
\end{equation}
By construction,$T(x)$ is a polynomial in $x$ with exponents from $0$ to $2L+2$ 
\begin{equation}
	\begin{split}
		T(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
	\end{split}
\end{equation}
where, for all $k\in\{0,\ldots,2L+2\}$, we call $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
\begin{equation}
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
\end{equation}
Arguing similarly we write the elements of $U_{0}(x)$ in a polynomial expansion as 
\begin{equation}
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
\end{equation}
 In the following we will study the charge expansion of $T^{\Delta}(x)$ when $x\to \infty$. As it will be clear in the following, only the first three coefficients for the diagonal elements and only the first one for the non-diagonal elements will be needed. Therefore, using \eqref{RURU}, we compute: 
\begin{itemize}
	\item For $D_{N,N}(x)$:

@@

Using \eqref{EX1}, \eqref{EX2} and \eqref{EX3} we obtain for every $i,j\in\{1,\ldots,N-1\}$ 

>>>>

We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename its elements, each of them acting on the quantum space $V$, has follows
		U_{0}(x)=\begin{pmatrix}
			D_{11}(x)&B_{2}(x)&\ldots&B_{N}(x)\\
			C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
			C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
	U_{0}(x)=\begin{pmatrix}
		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
The exchange relations for the elements of the above matrix can be found using \eqref{RURU} and they read:
	\item for every $i\in\{1,\ldots,N-1\}$
	\begin{equation}\label{EX1}
			D_{N,N}(y)B_{i}(y)&=f(x,y)D_{N,N}(x)B_{i}(y)+f_{1}(x,y)B_{i}(x)D_{N,N}(y)\\&+f_{2}(x,y)\left(B_{i}(x)D_{i,i}(y)+\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)\right)
	\begin{equation}\label{EX2}
			D_{i,i}(x)B_{i}(x)&=h(x,y)B_{i}(y)D_{i,i}(x)+h_{1}(x,y)B_{i}(x)D_{i,i}(y)\\&+h_{2}(x,y)B_{1}(x)D_{N,N}(y)+h_{3}(x,y)B_{i}(y)D_{N,N}(x)\\&+\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(x)D_{k,i}(y)+h_{4}(x,y)\sum_{k=1\,:\, k\neq i}^{N-1}B_{k}(y)D_{k,i}(x)
	\item  for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
	\begin{equation}\label{EX3}
			D_{j,j}(x)B_{i}(y)&=B_{i}(x)D_{j,j}(y)+\frac{1}{2}h_{3}(x,y)\left(B_{i}(y)D_{i,i}(x)-B_{i}(x)D_{i,i}(y)\right)
			\frac{1}{2}h_{3}(x,y)\left(B_{i}(x)D_{N,N}(y)-B_{i}(y)D_{N,N}(x)\right)
			h_{1}(x,y)\left(B_{j}(x)D_{j,i}(y)-B_{j}(y)D_{i,j}(x)\right)
			\frac{1}{2}h_{3}(x,y)\sum_{k=1\,:\,k\neq i,j}\left(B_{k}(y)D_{k,i}(x)-B_{k}(x)D_{k,i}(y)\right)
\item for every $i,j\in \{1,\ldots,N-1\}$ such that $i\neq j$
\begin{equation}\label{EX4}
		D_{i,j}(x)B_{i}(y)=&-(x-y)h_{1}(x,y)B_{i}(y)D_{i,j}(x)+f_{2}(x,y)\sum_{k=1\,:\,k\neq i}^{N-1}B_{k}(y)D_{k,j}(x)\\+&\frac{1}{(x-y)}\left(B_{j}(y)D_{i,i}(x)-B_{j}(x)D_{i,i}(y)\right)\\+&\frac{1}{2}h_{3}(x,y)\left((1+x-y)B_{j}(x)D_{N,N}(y)-B_{j}(y)D_{N,N}(x)\right)
\begin{equation}\label{EX5}
	D_{i,j}(x)B_{j}(y)=\frac{(x-y)}{(x-y-1)}B_{j}D_{i,j}(x)+\frac{1}{(y+1-x)}D_{i,j}(y)B_{j}(x)
\item  for every $i,j,k\in \{1,\ldots,N-1\}$ such that $i\neq j\neq k$
\begin{equation}\label{EX6}
	D_{i,j}(x)B_{k}(y)=B_{k}(y)D_{i,j}(x)+\frac{1}{(x-y)}\left(B_{k}(y)D_{j,i}(x)-B_{k}(x)D_{j,i}(y)\right)
	&f(x,y)=\frac{(x+y)(x-y-1)}{(x-y)(1+x+y)}&f_{1}(x,y)=\frac{(x+y)}{(x-y)(1+x+y)}\quad&f_{2}(x,y)=\frac{1}{(1+x+y)}\nonumber\\&h(x,y)=\frac{(1+x-y)(x+y+2)}{(x-y)(1+x+y)}
	&h_{1}(x,y)=-\frac{(x+y+2)}{(x-y)(1+x+y)}\quad&h_{2}(x,y)=\frac{(2+x-y)}{(x-y)(1+x+y)}\nonumber
	\\&h_{3}(x,y)=\frac{2}{(x-y)(1+x+y)}
\subsection{Charges}
The transfer matrix $T^{\Delta}(x)$ reads
		T^{\Delta}(x)=%tr_{0}&\left(\begin{pmatrix}
			%-x&0&0&\ldots&0&(N+2x)(\alpha_{1}-\beta_{1})\\
		%	0&-x&0&\ldots&0&(N+2x)(\alpha_{2}-\beta_{2})\\
		%	\vdots&\vdots&\ddots&\vdots&\vdots&\vdots\\
		%	0&0&0&\ldots&-x&(N+2x)(\alpha_{N-1}-\beta_{N-1})\\
		%	0&0&0&\ldots&0&N+x
	%	\end{pmatrix}\right.
	%	\;\;\;\begin{pmatrix}
	%		D_{1,1}(x)&D_{1,2}(x)&\ldots&D_{1,N-1}(x)&C_{1}(x)\\
	%		D_{2,1}(x)&D_{2,2}(x)&\ldots&D_{2,N-1}(x)&C_{2}(x)\\
	%		\vdots&\vdots&\ddots&\vdots&\vdots\\
	%		D_{N-1,1}&D_{N-1,2}&\ldots&D_{N-1,N-1}(x)&C_{N-1}\\
	%		B_{1}(x)&B_{2}(x)&\ldots&B_{N-1}(x)&D_{N,N}(x)
	%	\end{pmatrix}\right)\\
	%=&
	(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)+\sum_{i=1}^{N-1}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
By construction,$T(x)$ is a polynomial in $x$ with exponents from $0$ to $2L+2$ 
		T(x)=
		\sum_{k=0}^{2L+2}Q_{k}x^{k}
where, for all $k\in\{0,\ldots,2L+2\}$, we call $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 
	T_{0}(x)=(N+x)D_{N,N}(x)-\sum_{i=1}^{N-1}xD_{ii}(x)\quad\text{such that}\quad T(x)=T_{0}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)
Arguing similarly we write the elements of $U_{0}(x)$ in a polynomial expansion as 
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
 In the following we will study the charge expansion of $T^{\Delta}(x)$ when $x\to \infty$. As it will be clear in the following, only the first three coefficients for the diagonal elements and only the first one for the non-diagonal elements will be needed. Therefore, using \eqref{RURU}, we compute: 
	\item For $D_{N,N}(x)$:

@@

Using \eqref{EX1}, \eqref{EX2}, \eqref{EX3}, \eqref{EX4},\eqref{EX5} and \eqref{EX6} we obtain for every $i,j\in\{1,\ldots,N-1\}$ 
